---
title: "World map with flags"
author: "Bruno Ascenso"
date: "13 de Novembro de 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

This page contains week 2 assignment of the course Developing Data Products on Coursera.  

The instructions were: *Create a web page using R Markdown that features a map created with Leaflet*.  

So, I decided to create a world map with markers for the countries. Each marker has the country flag as icon. I couldn't easily find flags for a few countries and thus a few icons appear as **?** in the map.

Can you zoom to your own country? :)

## The map

Here is the code used.
```{r worldmap}
library(rvest)
library(leaflet)

#Country coordinates downloaded from here
countriesURL <- "https://developers.google.com/public-data/docs/canonical/countries_csv"

# Flags downloaded manually from here and stored in the 'flags' folder
# A few are not available, but most of them are which allows for a nice render of the map
flagsURL <- "http://flags.fmcdn.net/data/flags-mini.zip"


# Get the country data: webscrappping ==> table
htmlContent <- read_html(countriesURL)
tables <- html_nodes(htmlContent, "table")

theTable <- html_table(tables[1], fill = TRUE)
countriesDF <- theTable[[1]]

# Remove entries without lat and lng
countriesDF <- countriesDF[complete.cases(countriesDF), ]

# Build path for icon flags
countriesDF$icon <- apply(countriesDF, 1, function(x) paste("flags/", x[1], ".png", sep = ""))

# Generate the map
worldCountryMap <- leaflet() %>% addTiles() %>% 
    addMarkers(lat = countriesDF$latitude, lng = countriesDF$longitude, popup = countriesDF$name, 
               icon = icons(countriesDF$icon), clusterOptions = markerClusterOptions())

```

**And here is the map. Enjoy!**
```{r, echo = FALSE}
worldCountryMap
```

